---
title: "ERA enzyme analysis"
output: html_notebook
---



```{r, echo = FALSE, warning = FALSE}
library(ggplot2)
library(tidyr)
library(gridExtra)
library(reshape2)
library(lme4)
library(lmerTest)
library(lsmeans)
library(RColorBrewer)
library(dplyr)
```

```{r, echo= FALSE}
# theme function
theme_pub = function (base_size = 11, base_family = "Helvetica") {
    theme_grey(base_size = base_size, base_family = base_family) %+replace% 
        theme(
            axis.line.x = element_line(size = .5),
            axis.line.y = element_line(size = .5),
            panel.background = element_rect(fill = "white", colour = NA), 
            panel.border = element_rect(fill = NA, color = "black", size = .5), 
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), 
            strip.background = element_rect(fill = "grey85", 
                colour = "grey20"), 
            legend.key = element_rect(fill = "white", 
                colour = NA), complete = TRUE)
}
# Color palette
FertColors =  c("red", "green", "blue")

```


```{r, echo = FALSE, results = "hide"}
# Data wrangling
# Server version: # Tbl1 = read.csv("/home/bryan/ERA/Master.csv", header = TRUE)

Tbl1 = read.csv("/home/bryan/ERA/MasterLong.csv", header = TRUE)

Tbl1$Rep = as.factor(Tbl1$Rep)
Tbl1$Row = as.factor(Tbl1$Row)
Tbl1$Fert = as.factor(Tbl1$Fert)
Tbl1$PlotIndex = as.factor(Tbl1$PlotIndex)
Tbl1$ERA = as.factor(Tbl1$ERA)
Tbl1$Genotype = as.factor(Tbl1$Genotype)



#Primary plants (no untreated, no high/low density)
#Primary plants (no untreated, no high/low density)
Data = Tbl1 %>% filter(SeedTreatment == "Treated" & !Plant %in% c("1939-High", "1939-Low", "2011-High", "2011-Low") | Plant == "Bare")

# Table for seed treatment comparisons
Data.sc = Tbl1 %>% filter(Plant %in% c("1936", "1936U", "1984","1984U", "1953", "1953U", "2003", "2003U")) %>% 
  filter(Fert == "85")

Data.sc$Plant = droplevels(Data.sc$Plant)
Data.sc$Genotype = droplevels(Data.sc$Genotype)


Data$Plant = droplevels(Data$Plant)


# set plant levels by year
Data = Data %>%
                   # sort  dataframe
  mutate(Plant = reorder(Plant,R_Year),
         Genotype = reorder(Genotype, R_Year)) # reset your factor-column based on that order

Data.sc = Data.sc %>%
                   # sort  dataframe
  mutate(Plant = reorder(Plant,R_Year),
         Genotype = reorder(Genotype, R_Year)) # reset your factor-column based on that order

Data$Plant %>% unique

```
```{r, echo = FALSE}
require(cowplot)
```


# Enzyme analysis 
## Global enzyme anovas on time series core

Determine the relative influence of rhizosphere effect and time point on enzyme activity
* Subset to just bare soil and six core genotypes 
x 3 timepoints
x 4 reps 
= 

```{r, echo = FALSE}

# for core use just 85kgN, 
#be sure to run cell above to define data.long
Data.c = Data %>% filter(Plant %in% c("Bare", "1939", "1953", "1971", "1984", "2001", "2011") & Fert == "85" & !is.na(BG_activity.g))


Data.c$Plant = factor(Data.c$Plant, levels = c("Bare", "1939", "1953", "1971", "1984", "2001", "2011"))

Data.c = mutate(Data.c, Planted = ifelse(Plant == "Bare", "Bare", "Planted"))
        

```

Enzymes activity varied with data of sampling and the rhizosphere effect.  For LAP, a protease, there was a significant interaction between time of sampling and the rhizosphere effect. A rhizosphere effect was evident at the first sampling, but not at later dates

```{r}

# List = c("BG_activity.g", "BX_activity.g", "CB_activity.g", "LAP_activity.g", "NAG_activity.g")
# for (i in List) {
# m1 = lmer(log(get(i))~TimePoint*Planted + (1|Rep)  + (1|Rep:Row:Pos),  data = Data.c, na.action = na.exclude)
#   print(paste(i))
#   anova(m1, ddf = "Kenward-Roger") %>% print
#   plot(m1, title = paste(i)) %>% print
# }
# 

mBG = lmer(log(BG_activity.g)~TimePoint*Planted + (1|Rep) + (1|Genotype) + (1|Rep:Row:Pos),  data = Data.c, na.action = na.exclude)
  print("BG")
  anova(mBG, ddf = "Kenward-Roger") %>% print
  plot(mBG) %>% print


mBX = lmer(log(BX_activity.g)~TimePoint*Planted + (1|Rep) + (1|Genotype) + (1|Rep:Row:Pos),  data = Data.c, na.action = na.exclude)
print("BX")
  anova(mBX, ddf = "Kenward-Roger") %>% print
  plot(mBX) %>% print
  
mCB = lmer(log(CB_activity.g)~TimePoint*Planted + (1|Rep) + (1|Genotype) + (1|Rep:Row:Pos),  data = Data.c, na.action = na.exclude)
  print("CB")
  anova(mCB, ddf = "Kenward-Roger") %>% print
  plot(mCB) %>% print

mLAP= lmer(log(LAP_activity.g)~TimePoint*Planted + (1|Rep) + (1|Genotype) + (1|Rep:Row:Pos),  data = Data.c, na.action = na.exclude)
  print("LAP")
  anova(mLAP, ddf = "Kenward-Roger") %>% print
  plot(mLAP) %>% print
  
mNAG= lmer(log(NAG_activity.g)~TimePoint*Planted + (1|Rep) + (1|Genotype) + (1|Rep:Row:Pos),  data = Data.c, na.action = na.exclude)
  print("NAG")
  anova(mNAG, ddf = "Kenward-Roger") %>% print
  plot(mNAG) %>% print

```


## Plot core group rhizosphere effect through time
### Generate lsmeans 
```{r}
 BGcld.df = lsmeans(mBG, pairwise~Planted|TimePoint) %>%
        cld(Letters = c(letters))  %>% 
        as.data.frame %>% 
        filter(!is.na(lsmean)) %>%# required to drop unused ranks
        mutate(lsmean = exp(lsmean),
                                lower.CL = exp(lower.CL),
                                upper.CL = exp(upper.CL),
                                se = exp(SE),
                                # .group = ifelse(Fert == "Nneg", as.character(.group),
                                #                 toupper(.group)),
                                enzyme = "BG") 

 BXcld.df = lsmeans(mBX, pairwise~Planted|TimePoint) %>%
        cld(Letters = c(letters))  %>% 
        as.data.frame %>% 
        filter(!is.na(lsmean)) %>%# required to drop unused ranks
        mutate(lsmean = exp(lsmean),
                                lower.CL = exp(lower.CL),
                                upper.CL = exp(upper.CL),
                                se = exp(SE),
                                # .group = ifelse(Fert == "Nneg", as.character(.group),
                                #                 toupper(.group)),
                                enzyme = "BX") 
 
 CBcld.df = lsmeans(mCB, pairwise~Planted|TimePoint) %>%
        cld(Letters = c(letters))  %>% 
        as.data.frame %>% 
        filter(!is.na(lsmean)) %>%# required to drop unused ranks
        mutate(lsmean = exp(lsmean),
                                lower.CL = exp(lower.CL),
                                upper.CL = exp(upper.CL),
                                se = exp(SE),
                                # .group = ifelse(Fert == "Nneg", as.character(.group),
                                #                 toupper(.group)),
                                enzyme = "CB") 
  
   LAPcld.df = lsmeans(mLAP, pairwise~Planted|TimePoint) %>%
        cld(Letters = c(letters))  %>% 
        as.data.frame %>% 
        filter(!is.na(lsmean)) %>%# required to drop unused ranks
        mutate(lsmean = exp(lsmean),
                                lower.CL = exp(lower.CL),
                                upper.CL = exp(upper.CL),
                                se = exp(SE),
                                # .group = ifelse(Fert == "Nneg", as.character(.group),
                                #                 toupper(.group)),
                                enzyme = "LAP") 
   

   
   NAGcld.df = lsmeans(mNAG, pairwise~Planted|TimePoint) %>%
        cld(Letters = c(letters))  %>% 
        as.data.frame %>% 
        filter(!is.na(lsmean)) %>%# required to drop unused ranks
        mutate(lsmean = exp(lsmean),
                                lower.CL = exp(lower.CL),
                                upper.CL = exp(upper.CL),
                                se = exp(SE),
                                # .group = ifelse(Fert == "Nneg", as.character(.group),
                                #                 toupper(.group)),
                                enzyme = "NAG") 

Cld.df = bind_rows(BGcld.df, BXcld.df, CBcld.df,LAPcld.df, NAGcld.df)
```

### Create Plot
## Test rhizosphere effect at each time point for LAP
```{r}
head(Cld.df)
dodge = position_dodge(width=0.9)
P1 = ggplot(Cld.df, aes(x = Planted, y = lsmean, fill = Planted)) +
       # scale_shape_manual(values = c(21, 22)) +
        
        geom_bar(stat = "identity", position = dodge) + 
        geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                        position=dodge, width = 0.4, colour = "Black") +
        #geom_point(position = dodge, size = 3) + 
        ylab("Activity (nmol/g/s/hr)")+
        # #ggtitle("BG") +
        scale_fill_manual(values = c("grey", "black")) +
        #guides(fill=guide_legend(override.aes=list(colour= CoreColors_wBare))) +
        
        theme_pub()+
  
        theme(axis.title.x = element_blank(),
              axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1),
              legend.position = "none") +
  
        
        
        # # #theme(axis.title.y = element_blank()) +
        # # facet_wrap(~ Enzyme, scales = "free_y", ncol = 4)+
        # # theme(legend.position="none") +
        geom_text(aes(y = upper.CL + 2*(upper.CL-lsmean), label=.group), position = dodge)+
        facet_grid(enzyme ~ TimePoint, scales = "free_y")
P1    
```

```{r}
svg(filename = '/home/bryan/ERA/data/figures/ms_versions/EnzymeRhizosphereEffect.svg', width = 6.5, height = 6.5)
P1 
dev.off()
```


Conclusions:
Consistent rhizosphere effect for BG and BX.  Interestingly CB is somewhat more muted so that individual comparisons are not significant at R1 qand R3.  Nor is LAP significant at R1 or R3.


```{r}
sessionInfo()
```

